---
title: "Introduction to geysertimes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to geysertimes}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
```
```{r, hidden_values, echo=FALSE}
defpath <- "/tmp/RtmpvSGw5Y/GeyserTimes/2019-05-13/eruptions_data.rds"
recpath <- "/home/spk/.local/share/GeyserTimes/2019-05-13/eruptions_data.rds"
```

# Basic Use

Load the package other packages used in this vignette.
```{r library}
suppressPackageStartupMessages(library("dplyr"))
library("geysertimes")
```

## Get the Data

The `gt_get_data` function downloads the compressed eruptions data
from `https://geysertimes.org/archive/`,
reads the data compressed data into R
and saves version of the R object
in the location specified
in the `dest_folder` argument to the function.
The default location for `dest_folder` is
`file.path(tempdir(), "GeyserTimes"))`.
This default location is used to meet the CRAN requirement of
not writing files by default to any location other than under `tempdir()`.

```{r default_get, eval=FALSE}
defpath <- gt_get_data()
```
```{r default_get_print}
defpath
```

Users are encouraged to set `dest_folder` to the value given by
`gt_path()` which is a permanent location appropriate for the
user on the particular platform.

```{r gt_path}
gt_path()
```

If a permanent location is used, the user only needs to get the
data once.
Using the suggested value for `dest_folder`:
```{r recommend_path, eval=FALSE}
recpath <- gt_get_data(dest_folder=gt_path())
```
```{r recommend_path_print}
recpath
```

## Load the Data

The `gt_load_data` is used to load the saved R object.

```{r load01}
gtdata <- gt_load_data()
```

A quick look at the data:
```{r look}
dim(gtdata)
names(gtdata)
```

### Data Version
The data that is downloaded is versioned.
The version id is the date when the data was downloaded.

The `gt_version()` lists the latest version of the data that
has been downloaded.
Setting `all=TRUE` will list all versions of the data that have been
downloaded.

```{r version}
gt_version()
```

```{r version_all}
gt_version(all=TRUE)
```

## Simple Analysis

Geysers with the most recorded eruptions:
```{r eruptions_counts, tibble.print_max=20L}
print(n=20,
gtdata %>% group_by(geyser) %>% summarise(N=n()) %>% arrange(desc(N)))
```
